---
title: "DiBartolomeis et al 2019 Analysis"
author: "Allen Olmstead"
date: "November 22, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pdftools)
library(stringr)
library(readxl)
library(maps)
#library(socviz)
library(rvest)
library(httr)
library(jsonlite)
library(tidyverse)
```

Data for AITL (Acute Insecticide Toxicity Loading) came from the supplemental material of:  
DiBartolomeis M, Kegley S, Mineau P, Radford R, Klein K. 2019. An assessment of acute insecticide toxicity loading (AITL) of chemical pesticides used on agricultural land in the United States. PLoS ONE 14(8): e0220029 [link](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0220029)

```{r}
# read in DiBartolomeis et al 2019 supplemental pdf file
file1 <- "./Ecotox data files/pone.0220029.s001.pdf"

# function to start pdf page processing
import_pdf_step1 <- function(x, page) {
  pdf_text(x)[page] %>% 
  str_split("\n", simplify = TRUE) %>% 
  as.vector() %>% 
  enframe(name = NULL) %>% 
  filter(str_detect(value, "^\\w"))
}

# Column names for pdf table
s1_col_names <- c("pesticide", "half_life", "study_type", "citation1", "contact_ld50",
                  "oral_ld50", "citation2")

# read in first page of pdf file
s1_app_1 <- import_pdf_step1(file1, 1)  %>% 
  .[2:20, ] %>% 
  separate(value, 
           into = s1_col_names,
           sep = c(30, 40, 52, 65, 80, 88, 100))

# read in second page of pdf file
s1_app_2 <- import_pdf_step1(file1, 2)  %>% 
  separate(value, 
           into = s1_col_names,
           sep = c(25, 35, 48, 55, 65, 75, 100))

# read in third page of pdf file
s1_app_3 <- import_pdf_step1(file1, 3)  %>% 
  separate(value, 
           into = s1_col_names,
           sep = c(25, 30, 48, 55, 65, 72, 100))
# Note that Methiocarb values are missing
s1_app_3[startsWith(s1_app_3$pesticide, "Methio"), c(2, 5, 6)] <- c(35, 0.30, 0.47)

# read in fourth page of pdf file
s1_app_4 <- import_pdf_step1(file1, 4)  %>% 
  .[1:18, ] %>% 
  separate(value, 
           into = s1_col_names,
           sep = c(29, 42, 65, 75, 85, 100, 110))
# Note that Spinetoram values are missing
s1_app_4[startsWith(s1_app_4$pesticide, "Spine"), c(1:3, 5, 6)] <- 
  c("Spinetoram", 16.1, "EU Soil", 0.026, 0.082)
# Rename Spinosad
s1_app_4[startsWith(s1_app_4$pesticide, "Spinosad"), 1] <- "Spinosad"

# bind all pdf pages together and process data table
s1_app <- bind_rows(s1_app_1, s1_app_2, s1_app_3, s1_app_4) %>% 
  select(-citation1, -citation2) %>% 
  mutate_all(str_trim) %>% 
  mutate_at(vars(half_life, contact_ld50, oral_ld50), as.numeric) %>% 
  filter(pesticide != "L)")
```

Estimated annual agricultural pesticide use in the United States came for the Pesticide National Synthesis Project [link](https://water.usgs.gov/nawqa/pnsp/usage/maps/about.php) from the USGS. 

```{r, epest, message = FALSE}
# read in USGS EPest data
setwd("./USGS data files")
epest <- list.files(pattern = "EPest.county.estimates.*.txt") %>% 
  lapply(read_tsv) %>% 
  bind_rows() %>% 
  mutate(COMPOUND = str_to_title(COMPOUND),
         state = state.fips$polyname[match(as.numeric(STATE_FIPS_CODE), state.fips$fips)]) %>% 
  separate(state, into = c("state", "other"), sep = ":") %>% 
  select(-other)
  
colnames(epest) <- str_to_lower(colnames(epest))

# Correct some pesticide names
epest[epest$compound == "Bladprotein", "compound"] <- "Blad Protein"
epest[epest$compound == "Fluvalinate Tau", "compound"] <- "Fluvalinate-Tau"
epest[epest$compound == "Copper Sulf Tribasic", "compound"] <- "Copper Sulfate Tribasic"
epest[epest$compound == "Potassiumsilicate", "compound"] <- "Potassium Silicate"

# Summarize EPest at the State Level
epest_state <- epest %>%
  group_by(compound, year, state) %>% 
  summarise(epest_low_kg = sum(epest_low_kg, na.rm = TRUE),
            epest_high_kg = sum(epest_high_kg, na.rm = TRUE))

# Summarize EPest at the national level
epest_nation <- epest_state %>% 
  group_by(compound, year) %>% 
  summarize(epest_low_kg = sum(epest_low_kg, na.rm = TRUE),
            epest_high_kg = sum(epest_high_kg, na.rm = TRUE))

write.csv(epest_state, "epest_state.csv")
```

Mode of action information for insecticides was obtained from the Insecticide Resistance Action Committee [link](https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=2&ved=2ahUKEwi06MSLr5PmAhXo1FkKHaJRDx0QFjABegQIARAC&url=https%3A%2F%2Fwww.irac-online.org%2Fdocuments%2Fmoa-classification%2F&usg=AOvVaw3RUw6h_AeroMUm-sko9uGy)

```{r, irac_class}
# read in irac pdf file
file_irac <- "./Pesticide Class/_MoA-Classification_v9.3_13June19.pdf"

# function to import pdf pages
import_pdf <- function(x, page, rows, into, sep) {
  pdf_text(x)[page] %>% 
  str_split("\n", simplify = TRUE) %>% 
  as.vector() %>% 
  enframe(name = NULL) %>% 
  .[rows, ] %>% 
  separate(value, into = into, sep = sep)
}

# column names for irac table
irac_col_names <- c("compound1", "irac1", "compound2", "irac2")

# first page of irac table
irac_1 <- import_pdf(file_irac, 26, 10:66, irac_col_names, c(50, 60, 110, 210))
# Fix some entries that got split
irac_1[startsWith(irac_1$compound1, "Bioallethrin"), 2] <- "3A"
irac_1[startsWith(str_trim(irac_1$compound2), "Chenopodium"), 3:4] <- 
  c("Chenopodium ambrosioides extract", "UNE")  

# second page of irac table
irac_2 <- import_pdf(file_irac, 27, 5:47, irac_col_names, c(49, 60, 110, 210))
# Fix some split entries
irac_2[startsWith(str_trim(irac_2$compound1), "Fatty"), 1:4] <- 
  c("Fatty acid monoesters with glycerol or propanediol", "UNE",
    "Isopropyl )-(methoxyaminothiophosphoryl) salicylate", "1B")

# third page of irac table
irac_3 <- import_pdf(file_irac, 28, 5:52, irac_col_names, c(48, 60, 110, 210))
# Fix a split entry
irac_3[startsWith(str_trim(irac_3$compound1), "Paecilomyces"), 2] <- "UNF"

# fourth page of irac table
irac_4 <- import_pdf(file_irac, 29, 5:24, irac_col_names, c(48, 60, 110, 210))

# create irac dataset and process
irac <- bind_rows(irac_1[, 3:4], irac_2[, 3:4], irac_3[, 3:4], irac_4[, 3:4]) %>% 
  rename(compound1 = compound2, irac1 = irac2) %>% 
  bind_rows(irac_1[, 1:2], irac_2[, 1:2], irac_3[, 1:2], irac_4[, 1:2]) %>% 
  mutate_all(str_trim) %>% 
  rename(compound = compound1, irac = irac1) %>% 
  filter(compound != "" & irac != "") %>% 
  mutate(insecticide = TRUE,
         compound = str_to_title(compound)) %>% 
  arrange(compound)

# rename select pesticides to match USGS epest names
irac[irac$compound == "Alpha-Cypermethrin", "compound"] <- "Alpha Cypermethrin"
irac[irac$compound == "Aluminium Phosphide", "compound"] <- "Aluminum Phosphide"
irac[irac$compound == "Beauveria Bassiana Strains", "compound"] <- "Beauveria Bassiana"
irac[irac$compound == "Burkholderia Spp,", "compound"] <- "Burkholderia Spp"
irac[irac$compound == "Chenopodium Ambrosioides Extract", "compound"] <- 
  "Chenopodium Ambrosioides"
irac[irac$compound == "Demeton-S-Methyl", "compound"] <- "Demeton"
irac[irac$compound == "Emamectin Benzoate", "compound"] <- "Emamectin"
irac[irac$compound == "Flubendimide", "compound"] <- "Flubendiamide"
irac[irac$compound == "Pyrethrins (Pyrethrum)", "compound"] <- "Pyrethrins"
```

Mode of action information for fungicides was obtained from the Fungicide Resistance Action Committee [link](http://ipm.ifas.ufl.edu/resources/success_stories/T&PGuide/pdfs/Appendices/Appendix6-FRAC.pdf)

```{r, frac_class}
# read in frac pdf files
file_frac <- "./Pesticide Class/Appendix6-FRAC.pdf"

# column names for frac table
frac_col_names <- c("frac", "target", "group_name", "chem_group", "compound", "comments")

# process pdf pages
frac_1 <- import_pdf(file_frac, 3, 5:67, frac_col_names, c(5, 25, 43, 57, 78, 160))
frac_2 <- import_pdf(file_frac, 4, 4:62, frac_col_names, c(5, 25, 42, 58, 77, 160))
frac_3 <- import_pdf(file_frac, 5, 4:79, frac_col_names, c(4, 24, 42, 62, 82, 160))
frac_4 <- import_pdf(file_frac, 6, 4:71, frac_col_names, c(4, 24, 42, 62, 82, 160))
frac_5 <- import_pdf(file_frac, 7, 4:43, frac_col_names, c(4, 24, 42, 62, 85, 160))

# create frac list of compounds
frac <- bind_rows(frac_1, frac_2, frac_3, frac_4, frac_5) %>% 
  mutate_all(str_trim) %>%
  select(compound) %>% 
  filter(compound != "" & !compound %in% c("salts", "(Bactericide)", "(also antibacterial and",
                                           "antifungal activity)"))
# rename a couple of problematic rows
frac[startsWith(frac$compound, "(=mefenoxam"), 1] <- "mefenoxam"
frac[startsWith(frac$compound, "phophorous acid"), 1] <- "phosphorous acid and salts"

# create tibble with just the irac codes
frac_code <- tibble(frac = as.character(c(rep(1, 6), rep(2, 4), rep(3, 34), rep(4, 7), rep(5, 7),
                             rep(6, 4), rep(7, 10), rep(8, 3), rep(9, 3), 10, rep(11, 12),
                             12, 12, 13, rep(14, 7), rep(16.1, 3), rep(16.2, 3), 17,
                             rep(18, 3), 19, 20:27, rep(28, 3), rep(29, 4), rep(30, 3), 31,
                             32, 32, 33, 33:39, rep(40, 5), 41, 42, rep("P", 3))))

# create tibble with just the fungicide group names
fung_group <- tibble(fungicide_group = c(rep("benzimidazoles", 4), rep("thiophanates", 2),
                                         rep("dicarboximides", 4), rep("imidazoles", 5),
                                         "piperazines", "pyridines", rep("pyrimidines", 2),
                                         rep("trizaoles", 25), rep("acylalanines", 5),
                                         "oxazolidinones", "butyrolactones",
                                         rep("morpholines", 4), rep("piperidines", 2),
                                         "spiroketalamines", rep("phosphorothiolates", 3),
                                         "dithiolanes", rep("carboxamides", 10),
                                         rep("hydroxy-(2-amino-)pyrimidines", 3),
                                         rep("anilinopyrimidines", 3), "n-phenylcarbamates",
                                         rep("methoxyacrylates", 3), "methoxycarbamates",
                                         rep("oximino acetates", 2),
                                         rep("oximino acetamides", 3), "oxazolidine-diones",
                                         "dihydro-dioxaines", "imidazolinones",
                                         rep("phenylpyrroles", 2), "quinolones",
                                         rep("aromatic hydrocarbons", 6), "heteroaromatics",
                                         "isobenzofuranone", "pyrroloquinolinone", 
                                         "thiazolobenzothiazole", "cyclopropanecarboxamide",
                                         "carboxamide", "propionamide", "hydroxyanilides",
                                         "thiocarbamates", rep("allylamines", 2),
                                         "peptidyl pyrimidine nucleoside", "phenylureas",
                                         "cyanoimidazole", "benzamides",
                                         "enopyranuronic acid antibiotic",
                                         "hexopyranosyl antibiotic",
                                         rep("glucopyranosyl antibiotic",2),
                                         "cyanoacetamide-oximes", rep("carbamates", 3),
                                         rep("dinitrophenyl crotonates", 2), 
                                         "primidinonehydrazones", "2,6-dinitroanilines",
                                         rep("tri phenyl tin compounds", 3), "carboxylic acids",
                                         rep("heteroaromatics", 2), "ethyl phosphonates", 
                                         "phosphonates", "phthalamic acids", "benzotriazines",
                                         "benzenesulfonamides", "pyridazinones",
                                         "thiophenecarboxamides", "pyrimidinamides",
                                         rep("cinnamic acid", 2), 
                                         rep("valinamide carbamates", 2), "mandelic acid amides",
                                         "tetracycline antibiotic", "thiocarbamate",
                                         "benzo-thiadiazole", "benzisothiazole",
                                         "thiadiazolecarboxamide"))

# create frac data set by binding frac codes, chemical groups and compound names
frac <- bind_cols(frac_code, fung_group, frac) %>% 
  mutate(compound = str_to_title(compound),
         fungicide = TRUE)

# rename select pesticides to match USGS epest names
frac[frac$compound == "Acibenzolar-S-Methyl", "compound"] <- "Acibenzolar"
frac[frac$compound == "Fosetyl-Al", "compound"] <- "Fosetyl"
frac[frac$compound == "Hymexazole", "compound"] <- "Hymexazol"
frac[frac$compound == "Propamocarb", "compound"] <- "Propamocarb Hcl"
frac[frac$compound == "Quintozene (Pcnb)", "compound"] <- "Quintozene"
```

Mode of action information for herbicides was obtained from the Herbicide Resistance Action Committee [link](http://www.weedscience.org/Documents/ShowDocuments.aspx?DocumentID=1193)

```{r, hrac}
# read in frac pdf files
file_hrac <- "./Pesticide Class/WeedScienceCom.pdf"

# column names for hrac table
hrac_col_names <- c("hrac", "site_of_action", "herbicide_group", "compound", "wssa_group")

# read in hrac pdf pages
hrac_1 <- import_pdf(file_hrac, 1, 28:83, hrac_col_names, c(25, 65, 110, 155, 170))
hrac_2 <- import_pdf(file_hrac, 2, 2:85, hrac_col_names, c(15, 56, 82, 104, 170))
# fix a split entry
hrac_2[startsWith(str_trim(hrac_2$herbicide_group), "Sulfonylamino"), 3] <-
  "Sulfonylaminocarbonyltriazolinone"
hrac_2[startsWith(str_trim(hrac_2$herbicide_group), "triazolinone"), 3] <- NA
hrac_3 <- import_pdf(file_hrac, 3, 2:71, hrac_col_names, c(15, 69, 90, 115, 170))
hrac_4 <- import_pdf(file_hrac, 4, 2:77, hrac_col_names, c(15, 74, 99, 129, 170))
hrac_5 <- import_pdf(file_hrac, 5, 2:20, hrac_col_names, c(15, 74, 99, 120, 170))
# add a classification for WSSA for the last group
hrac_5[str_trim(hrac_5$compound) == "bromobutide", 5] <- 27

# create hrac dataset of compounds
hrac <- bind_rows(hrac_1, hrac_2, hrac_3, hrac_4, hrac_5) %>% 
  mutate_all(str_trim) %>% 
  select(-site_of_action) %>% 
  filter(hrac != "Group" & hrac != "HRAC") %>% 
  mutate(hrac = ifelse(lead(hrac) != "", lead(hrac), NA),
         wssa_group = ifelse(lead(wssa_group) != "", lead(wssa_group), NA),
         herbicide_group = ifelse(herbicide_group %in% c("", "\u2018FOPs\u2019", 
                                                         "\u2018DIMs\u2019"),
                                  NA, herbicide_group)) %>% 
  fill(hrac, wssa_group, herbicide_group) %>% 
  filter(compound != "" & !compound %in% c("...", "(in vivo inhibition of", "lycopene cyclase)",
                                           "(also group O)", "(also group L)")) %>% 
  mutate(compound = str_to_title(compound),
         herbicide = TRUE)

# rename select pesticides to match USGS epest names
hrac[hrac$compound == "Acifluorfen-Na", "compound"] <- "Acifluorfen"
hrac[hrac$compound == "Ametryne", "compound"] <- "Ametryn"
hrac[hrac$compound == "Benefin = Benfluralin", "compound"] <- "Benfluralin"
hrac[hrac$compound == "Bensulfuron-Methyl", "compound"] <- "Bensulfuron"
hrac[hrac$compound == "Bentazon", "compound"] <- "Bentazone"
hrac[hrac$compound == "Bispyribac-Na", "compound"] <- "Bispyribac"
hrac[hrac$compound == "Clodinafop-Propargyl", "compound"] <- "Clodinafop"
hrac[hrac$compound == "Cyhalofop-Butyl", "compound"] <- "Cyhalofop"
hrac[hrac$compound == "Dcpa = Chlorthal-Dimethyl", "compound"] <- "Dcpa"
hrac[hrac$compound == "Dichlorprop = 2,4-Dp", "compound"] <- "Dichlorprop"
hrac[hrac$compound == "Diclofop-Methyl", "compound"] <- "Diclofop"
hrac[hrac$compound == "Diflufenzopyr-Na", "compound"] <- "Diflufenzopyr"
hrac[hrac$compound == "Dimethanamid", "compound"] <- "Dimethenamid"
hrac[hrac$compound == "Ethametsulfuron-Methyl", "compound"] <- "Ethametsulfuron"
hrac[hrac$compound == "Fenoxaprop-P-Ethyl", "compound"] <- "Fenoxaprop"
hrac[hrac$compound == "Fluazifop-P-Butyl", "compound"] <- "Fluazifop"
hrac[hrac$compound == "Flucarbazone-Na", "compound"] <- "Flucarbazone"
hrac[hrac$compound == "Flumiclorac-Pentyl", "compound"] <- "Flumiclorac"
hrac[hrac$compound == "Glufosinate-Ammonium", "compound"] <- "Glufosinate"
hrac[hrac$compound == "Halosulfuron-Methyl", "compound"] <- "Halosulfuron"
hrac[hrac$compound == "Imazamethabenz-Methyl", "compound"] <- "Imazamethabenz"
hrac[hrac$compound == "Mecoprop = Mcpp = Cmpp", "compound"] <- "Mecoprop"
hrac[hrac$compound == "Metam", "compound"] <- "Metam Potassium"
hrac[hrac$compound == "Metsulfuron-Methyl", "compound"] <- "Metsulfuron"
hrac[hrac$compound == "Primisulfuron-Methyl", "compound"] <- "Primisulfuron"
hrac[hrac$compound == "Prometryne", "compound"] <- "Prometryn"
hrac[hrac$compound == "Propoxycarbazone-Na", "compound"] <- "Propoxycarbazone"
hrac[hrac$compound == "Propyzamide = Pronamide", "compound"] <- "Propyzamide"
hrac[hrac$compound == "Pyraflufen-Ethyl", "compound"] <- "Pyraflufen Ethyl"
hrac[hrac$compound == "Pyrithiobac-Na", "compound"] <- "Pyrithiobac-Sodium"
hrac[hrac$compound == "Quizalofop-P-Ethyl", "compound"] <- "Quizalofop"
hrac[hrac$compound == "Sulfometuron-Methyl", "compound"] <- "Sulfometuron"
hrac[hrac$compound == "Terbutryne", "compound"] <- "Terbutryn"
hrac[hrac$compound == "Thifensulfuron-Methyl", "compound"] <- "Thifensulfuron"
hrac[hrac$compound == "Thiobencarb = Benthiocarb", "compound"] <- "Thiobencarb"
hrac[hrac$compound == "Triallate", "compound"] <- "Tri-Allate"
hrac[hrac$compound == "Tribenuron-Methyl", "compound"] <- "Tribenuron Methyl"
hrac[hrac$compound == "Triflusulfuron-Methyl", "compound"] <- "Triflusulfuron"
```

http://cru66.cahe.wsu.edu/labels/Dictionaries.php?dictionary=INGR

Additional info from:
https://sitem.herts.ac.uk/aeru/ppdb/en/index.htm


```{r, rac}
# Read in RAC codes for pesticide list
rac <- "http://cru66.cahe.wsu.edu/labels/Dictionaries.php?dictionary=INGR" %>% 
  read_html() %>% 
  html_nodes("table") %>% 
  .[2] %>% 
  html_table(header = TRUE, fill = TRUE) %>% 
  .[[1]] %>% 
  transmute(compound = gsub(" \\(.*\\)", "", str_to_title(Name)),
            rac_type = `Resistance Source`,
            rac_code = `Resistance Code`) %>% 
  mutate(compound = gsub(" -Historical Tol Code-", "", compound))

# Work read in
rac <- read_csv("./Pesticide Class/RAC WSU.csv") %>% 
  transmute(compound = gsub(" \\(.*\\)", "", str_to_title(Name)),
            rac_type = `Resistance Source`,
            rac_code = `Resistance Code`) %>% 
  mutate(compound = gsub(" -Historical Tol Code-", "", compound))

# rename select pesticides to match USGS epest names
rac[rac$compound == "Acibenzolar-S-Methyl", "compound"] <- "Acibenzolar"
rac[rac$compound == "Acifluorfen, Sodium Salt", "compound"] <- "Acifluorfen"
rac[rac$compound == "Alpha-Cypermethrin", "compound"] <- "Alpha Cypermethrin"
rac[rac$compound == "Ametoctradin", "compound"] <- "Amectoctradin"
rac[rac$compound == "Ametryne", "compound"] <- "Ametryn"
rac[rac$compound == "Bacillus Amyloliquefaciens, Strain F727", "compound"] <- 
  "Bacillus Amyloliquifacien"
rac[rac$compound == "Bacillus Mycoides, Isolate J", "compound"] <- "Bacillus Mycoides"
rac[rac$compound == "Bacillus Subtilis, Strain Gb03", "compound"] <- "Bacillus Subtilis"
rac[rac$compound == "Bacillus Thuringiensis Endotoxins", "compound"] <- "Bacillus Thuringiensis"
rac[rac$compound == "Benefin", "compound"] <- "Benfluralin"
rac[rac$compound == "Bentazon", "compound"] <- "Bentazone"
rac[rac$compound == "Benzovindiflupyr", "compound"] <- "Benzovidiflupyr"
rac[rac$compound == "Bispyribac-Sodium", "compound"] <- "Bispyribac"
rac[rac$compound == "Blad", "compound"] <- "Blad Protein"
rac[rac$compound == "Chlorimuron-Ethyl", "compound"] <- "Chlorimuron"
rac[rac$compound == "Clodinafop-Propargyl", "compound"] <- "Clodinafop"
rac[rac$compound == "Copper As Elemental", "compound"] <- "Copper"
rac[rac$compound == "Cyhalothrin, Gamma", "compound"] <- "Cyhalothrin-Gamma"
rac[rac$compound == "Diclofop-Methyl", "compound"] <- "Diclofop"
rac[rac$compound == "Diflufenzopyr - Sodium", "compound"] <- "Diflufenzopyr"
rac[rac$compound == "Emamectin Benzoate", "compound"] <- "Emamectin"
rac[rac$compound == "Endothall", "compound"] <- "Endothal"
rac[rac$compound == "Fenbutatin-Oxide", "compound"] <- "Fenbutatin Oxide"
rac[rac$compound == "Fenoxaprop-P-Ethyl", "compound"] <- "Fenoxaprop"
rac[rac$compound == "Fluazifop-P-Butyl", "compound"] <- "Fluazifop"
rac[rac$compound == "Flucarbazone-Sodium", "compound"] <- "Flucarbazone"
rac[rac$compound == "Flumiclorac, Pentyl Ester", "compound"] <- "Flumiclorac"
rac[rac$compound == "Formetanate Hydrochloride", "compound"] <- "Formetanate"
rac[rac$compound == "Fosamine Ammonium", "compound"] <- "Fosamine"
rac[rac$compound == "Fosetyl Al", "compound"] <- "Fosetyl"
rac[rac$compound == "Glufosinate-Ammonium", "compound"] <- "Glufosinate"
rac[rac$compound == "Halauxifen-Methyl", "compound"] <- "Halauxifen"
rac[rac$compound == "Halosulfuron-Methyl", "compound"] <- "Halosulfuron"
rac[rac$compound == "Imazamethabenz-Methyl", "compound"] <- "Imazamethabenz"
rac[rac$compound == "Iodosulfuron-Methyl-Sodium", "compound"] <- "Iodosulfuron"
rac[rac$compound == "Mesosulfuron-Methyl", "compound"] <- "Mesosulfuron"
rac[rac$compound == "Metsulfuron-Methyl", "compound"] <- "Metsulfuron"
rac[rac$compound == "Oxydemeton Methyl", "compound"] <- "Oxydemeton-Methyl"
rac[rac$compound == "Primisulfuron-Methyl", "compound"] <- "Primisulfuron"
rac[rac$compound == "Propamocarb Hydrochloride", "compound"] <- "Propamocarb Hcl"
rac[rac$compound == "Propoxycarbazone-Sodium", "compound"] <- "Propoxycarbazone"
rac[rac$compound == "Pyraflufen-Ethyl", "compound"] <- "Pyraflufen Ethyl"
rac[rac$compound == "Quizalofop-P Ethyl", "compound"] <- "Quizalofop"
rac[rac$compound == "Spinosad", "compound"] <- "Spinosyn"
rac[rac$compound == "Sulfometuron-Methyl", "compound"] <- "Sulfometuron"
rac[rac$compound == "Terbutryne", "compound"] <- "Terbutryn"
rac[rac$compound == "Thifensulfuron-Methyl", "compound"] <- "Thifensulfuron"
rac[rac$compound == "Thiophanate Methyl", "compound"] <- "Thiophanate-Methyl"
rac[rac$compound == "Triallate", "compound"] <- "Tri-Allate"
rac[rac$compound == "Tribenuron-Methyl", "compound"] <- "Tribenuron Methyl"
rac[rac$compound == "Triflusulfuron-Methyl", "compound"] <- "Triflusulfuron"
rac[rac$compound == "Tau-Fluvalinate", "compound"] <- "Fluvalinate-Tau"
rac[rac$compound == "Lime Sulfur - Calcium Polysulfide", "compound"] <- "Calcium Polysulfide"
rac[rac$compound == "Pyrazon", "compound"] <- "Chloridazon"
rac[rac$compound == "Copper Sulfate Anhydrous", "compound"] <- "Copper Sulfate"
rac[rac$compound == "Copper Sulfate Basic", "compound"] <- "Copper Sulfate Tribasic"
rac[rac$compound == "2,4-Dp", "compound"] <- "Dichlorprop"
rac[rac$compound == "Dcna", "compound"] <- "Dicloran"
rac[rac$compound == "Ethoprop", "compound"] <- "Ethoprophos"
rac[rac$compound == "Polyoxin D Zinc Salt", "compound"] <- "Polyoxorim"
rac[rac$compound == "Pcnb", "compound"] <- "Quintozene"

# Include additional pesticides
rac <- rbind(rac, c("Amitrole", "HRAC", "F3"), 
             c("Barium Polysulfide", "FRAC", "NC"),
             c("Bensulfuron", "HRAC", "B"), 
             c("Bifenox", "HRAC", "E"),
             c("Bordeaux Mixture", "FRAC", "M1"), 
             c("Chinomethionat", "FRAC", "M10"),
             c("Chloramben", "HRAC", "O"), 
             c("Chlordimeform", "IRAC", "NC"),
             c("Ammonium Sulfamate", "HRAC", "NC"), 
             c("Copper Oxychloride S", "FRAC", "M1"),
             c("Cuprous Oxide", "FRAC", "M1"),
             c("Cyhalofop", "HRAC", "A"),
             c("Cyhalothrin-Lambda", "IRAC", "3"),
             c("Dalapon", "HRAC", "N"),
             c("Di-Allate", "HRAC", "N"),
             c("Diclosulam", "HRAC", "B"),
             c("Dienochlor", "IRAC", "2A"),
             c("Diethatyl", "HRAC", "K3"),
             c("Dimethenamid & Dimethenamid-P", "HRAC", "K3"),
             c("Dimethyl Disulfide", "IRAC", "NC"),
             c("Dinoseb", "HRAC", "M"),
             c("Dnoc", "HRAC", "M"),
             c("Dsma", "HRAC", "NC"),
             c("Epn", "IRAC", "1B"),
             c("Fensulfothion", "IRAC", "1B"),
             c("Fentin", "FRAC", "30"),
             c("Flucythrinate", "IRAC", "3"),
             c("Fluometuron", "HRAC", "C2/F3"),
             c("Flusilazole", "FRAC", "3"),
             c("Fluvalinate", "IRAC", "3"),
             c("Gallex", "FRAC", "NC"), 
             c("Gamma Aminobutyric Acid", "FRAC", "NC"),
             c("Garlic Juice", "IRAC", "NC"), 
             c("Gentamicin Sulfate", "FRAC", "NC"),
             c("Hydrated Lime", "IRAC", "NC"),
             c("Isazofos", "IRAC", "1B"),
             c("Isopropalin", "HRAC", "NC"),
             c("Kaolin Clay", "IRAC", "NC"),
             c("Kinoprene", "IRAC", "7A"),
             c("Lead Arsenate", "IRAC", "NC"),
             c("Mecoprop", "HRAC", "O"),
             c("Metam", "HRAC", "Z"),
             c("Metam Potassium", "HRAC", "Z"),
             c("Methyl Iodide", "IRAC", "NC"),
             c("Metolachlor-S", "HRAC", "K3"),
             c("Metolachlor & Metolachlor-S", "HRAC", "K3"),
             c("Molinate", "HRAC", "N"),
             c("Naptha", "HRAC", "NC"),
             c("Noruron", "HRAC", "NC"),
             c("Orthosulfamuron", "HRAC", "NC"),
             c("Petroleum Distillate", "FRAC", "NC"),
             c("Petroleum Oil", "FRAC", "NC"),
             c("Pinolene", "Adjuvant", "NC"),
             c("Potassium Carbonate", "FRAC", "NC"),
             c("Profenofos", "IRAC", "1B"),
             c("Profluralin", "HRAC", "NC"),
             c("Propyzamide", "HRAC", "K1"),
             c("Pyrithiobac-Sodium", "HRAC", "B"),
             c("Ryanodine", "IRAC", "28"),
             c("Sabadilla", "IRAC", "NC"), 
             c("Silicates", "FRAC", "NC"),
             c("Sodium Arsenite", "HRAC", "NC"),
             c("Sulfallate", "HRAC", "N"),
             c("Tca", "HRAC", "N"),
             c("Tebupirimphos", "IRAC", "1B"),
             c("Tetraborohydrate", "IRAC", "NC"),
             c("Tetrathiocarbonate", "FRAC", "NC"),
             c("Thidiazuron", "HRAC", "E"),
             c("Thiobencarb", "HRAC", "N"),
             c("Tribufos", "HRAC", "NC"),
             c("Tridiphane", "HRAC", "NC"),
             c("Trifloxysulfuron", "HRAC", "B"),
             c("Trimethacarb", "IRAC", "1A"),
             c("Burkholderia Cepacia", "IRAC", "UNB"),
             c("Burkholderia Spp", "IRAC", "UNB"),
             c("Chenopodium Ambrosioides", "IRAC", "UNE"),
             c("Beauveria Bassiana", "IRAC", "UNF"),
             c("Ampelomyces Quisqualis", "FRAC", "NC"),
             c("Aspergillus Flavus", "FRAC", "NC"),
             c("Aureobasidium Pullulans", "FRAC", "NC"),
             c("Bacillus Firmus", "IRAC", "NC"),
             c("Bacillus Pumilis", "FRAC", "NC"),
             c("Bacteriophage", "FRAC", "NC"),
             c("Chromobacterium Subtsugae", "IRAC", "NC"),
             c("Collectotrichum Spores", "HRAC", "NC"),
             c("Coniothyrium Minitans", "FRAC", "NC"),
             c("Cydia Pomonella", "IRAC", "NC"),
             c("Gliocladium Virens", "FRAC", "NC"), 
             c("Isaria Fumosorosea", "IRAC", "NC"),
             c("Myrothecium Verrucaria", "IRAC", "NC"),
             c("Nosema Locustae Cann", "IRAC", "NC"),
             c("Paecilomyces Lilacinus", "IRAC", "NC"),
             c("Phytophthora Spores", "HRAC", "NC"),
             c("Polyhedrosis Virus", "IRAC", "NC"),
             c("Pseudomonas Fluorescens", "FRAC", "NC"),
             c("Steinernema Carpocap", "IRAC", "NC"),
             c("Steinernema Riobravi", "IRAC", "NC"),
             c("Streptomyces Lydicus", "FRAC", "NC"))

# Add missing RAC information 
rac[rac$compound == "Allyl Isothiocyanate", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Barban", 2:3] <- c("HRAC", "NC")
rac[rac$compound == "Bendiocarb", 2:3] <- c("IRAC", "1A")
rac[rac$compound == "Carbophenothion", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Chlorobenzilate", 2:3] <- c("IRAC", "2A")
rac[rac$compound == "Cinnamaldehyde", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Demeton", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Dichlone", 2:3] <- c("FRAC", "NC")
rac[rac$compound == "Dichloropropene", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Ethion", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Fluchloralin", 2:3] <- c("HRAC", "NC")
rac[rac$compound == "Fluensulfone", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Fonofos", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Harpin Protein", 2:3] <- c("FRAC", "NC")
rac[rac$compound == "Hydrogen Peroxide", 2:3] <- c("FRAC", "NC")
rac[rac$compound == "Isofenphos", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Lindane", 2:3] <- c("IRAC", "2A")
rac[rac$compound == "Metaldehyde", 2:3] <- c("Molluscicide", "NC")
rac[rac$compound == "Methazole", 2:3] <- c("HRAC", "Z")
rac[rac$compound == "Methyl Isothiocyanate", 2:3] <- c("FRAC", "NC")
rac[rac$compound == "Mevinphos", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Monocrotophos", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Neem Oil", 2:3] <- c("IRAC", "UNE")
rac[rac$compound == "Phosalone", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Phosphamidon", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Phosphoric Acid", 2:3] <- c("FRAC", "33")
rac[rac$compound == "Piperonyl Butoxide", 2:3] <- c("Adjuvant", "NC")
rac[rac$compound == "Potassium Oleate", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Potassium Silicate", 2:3] <- c("FRAC", "NC")
rac[rac$compound == "Saflufenacil", 2:3] <- c("HRAC", "E")
rac[rac$compound == "Sodium Chlorate", 2:3] <- c("HRAC", "NC")
rac[rac$compound == "Sodium Metaborate", 2:3] <- c("HRAC", "NC")
rac[rac$compound == "Spinetoram", 2:3] <- c("IRAC", "5")
rac[rac$compound == "Sucrose Octanoate", 2:3] <- c("IRAC", "NC")
rac[rac$compound == "Sulfur", 2:3] <- c("FRAC", "M2")
rac[rac$compound == "Sulfuric Acid", 2:3] <- c("HRAC", "NC")
rac[rac$compound == "Sulprofos", 2:3] <- c("IRAC", "1B")
rac[rac$compound == "Triazamate", 2:3] <- c("IRAC", "1A")
rac[rac$compound == "Zinc", 2:3] <- c("FRAC", "NC")
```


```{r}
# Vector of Plant Growth Regulators
pgr <- tibble(compound = c("1-Methyl Cyclopropene", "Chlormequat", "Cytokinin", 
                           "Daminozide", "Ethephon", "Gibberellic Acid", 
                           "Indolyl-Butyric Acid", "Maleic Hydrazide", "Mefluidide", 
                           "Mepiquat", "Decan-1-Ol", "Paclobutrazol", "Prohexadione", 
                           "Trinexapac", "Uniconazole", "Naphthylacetamide", 
                           "Naphthylacetic Acid", "6-Benzyladenine", "Abscisic Acid",
                           "Aviglycine", "Arsenic Acid", "Calcium Chloride", "Cppu",
                           "Cyanamide", "Cyclanilide", "Dimethipin",
                           "Dimethylarsinic Acid", "Fatty Alcohols", "Flumetralin",
                           "Hydroxypropanoic Acid", "Iba", "L-Glutamic Acid",
                           "Prohydrojasmon", "Sulfcarbamide", "Tetraoxosulfate", 
                           "Bacillus Cereus")) %>% 
  mutate(pgr = TRUE)

unique_epest <- tibble(compound = unique(epest_state$compound)) %>% 
  left_join(rac, by = "compound") %>% 
  left_join(pgr, by = "compound")

b <- unique_epest %>% 
  filter(is.na(rac_code), is.na(pgr)) 
```


Cropland Data Layer (CDL) was obtained fromthe USDA National Agricultural Statistics Service. [link](https://www.nass.usda.gov/Research_and_Science/Cropland/sarsfaqs2.php#Section1_10.0)

```{r, cdl}
read_cdl <- function(yr) {
  path <- paste0("./CDL/CropScape_", yr, "_Stats.xlsx")
  
  path %>% 
    excel_sheets() %>% 
    set_names() %>% 
    map_df(~ read_xlsx(path = path, sheet = .x, range = cell_cols("A:D")),
         .id = "state") %>% 
    rename(category = Category, acreage = Acreage) %>% 
    filter(!is.na(category), 
           Value != 64,        # Remove unused Shrubland(64) category
           Value != 65) %>%   # Remove unused Barren(65) category
    select(state, category, acreage) %>% 
    mutate(year = yr, state = tolower(state))
}

cdl <- bind_rows(lapply(2008:2018, read_cdl))

cdl_zero <- cdl %>%
  filter(state == "national") %>% 
  group_by(category) %>% 
  summarize(acres = sum(acreage)) %>% 
  filter(acres == 0)

cdl <- filter(cdl, !category %in% cdl_zero$category)

write.csv(cdl, "cdl.csv")
```

```{r}
bip <- read_html("https://bip2.beeinformed.org/loss-map/") %>% 
  html_nodes(xpath = "//*[@id='config']") %>% 
  html_text() %>% 
  fromJSON() %>% 
  .[[2]] %>% 
  as_tibble()

write.csv(bip, "bip.csv")
bip <- read_csv("bip.csv")
```

